Manuscript

### 2015-02-03 inst/simulation/manuscript.Rmd
...

prettyScenario <- function(scenario) substr(scenario, 1, 1)
prettyModelName <- function(x) {
  lookup <- data.frame(x=modelNames, y=c("ST", "T", "T2", "I"), stringsAsFactors=F)
  lookup$y[match(x, lookup$x)]
}

@@

  print(p)
  return(p)
}

#p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[1]), subset(logMeanPopulationSizes, modelName==modelNames[1]), modelName=modelNames[1], xlim=xlim, ylim=ylim)
#saveFigure(p, "manuscript-figure-3a1.png", width=8, height=4)

#xlim <- log10(10^c(0,6)); ylim <- xlim
#p <- plotLogPopulationSize(subset(logPopulationSizes10Days, modelName==modelNames[2]), subset(logMeanPopulationSizes10Days, modelName==modelNames[2]), modelName=modelNames[2], xlim=xlim, ylim=ylim)
#saveFigure(p, "manuscript-figure-3c2.png", width=8, height=4)
```

```{r figure-3-init-2}
registerDoMC(cores=10) # The nodes seem to run out of memory and fail with a bogus error message, so it's better to reduce the number of used cores.

populationSizes <- getPopulationSizes(scenarios=scenarios, modelNames=modelNames)
populationSizes2000 <- getPopulationSizes(scenarios=paste0(scenarios, "combined"), modelNames=modelNames)
populationSizes10Days <- getPopulationSizes(scenarios=paste0(scenarios, "10days"), modelNames=modelNames)

@@

```{r figure-3abc}
xlim <- log10(10^c(0,4)); ylim <- xlim
p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[1]), subset(logMeanPopulationSizes, modelName==modelNames[1]), modelName=modelNames[1], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3a1.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[2]), subset(logMeanPopulationSizes, modelName==modelNames[2]), modelName=modelNames[2], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3a2.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[3]), subset(logMeanPopulationSizes, modelName==modelNames[3]), modelName=modelNames[3], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3a3.png", width=8, height=4)

@@

dir <- normalizePath(context$figuresDirectory)
table1 <- getPopulationSizesTable(populationSizes, meanPopulationSizes, overEstimate=2000)
logTable1 <- getPopulationSizesTable(logPopulationSizes, logMeanPopulationSizes, overEstimate=log10(2000+1), file=file.path(dir, "table-1a.csv"))
logTable1$MeanProp <- table1$MeanProp; logTable1$SDProp <- table1$SDProp; 
write.csv(logTable1, file=file.path(dir, "table-1a.csv"))

table2 <- getPopulationSizesTable(populationSizes2000, meanPopulationSizes2000, overEstimate=20000)
logTable2 <- getPopulationSizesTable(logPopulationSizes2000, logMeanPopulationSizes2000, overEstimate=log10(20000+1), file=file.path(dir, "table-1b.csv"))
logTable2$MeanProp <- table2$MeanProp; logTable2$SDProp <- table2$SDProp; 
write.csv(logTable2, file=file.path(dir, "table-2a.csv"))

table3 <- getPopulationSizesTable(populationSizes10Days, meanPopulationSizes10Days, overEstimate=2000)
logTable3 <- getPopulationSizesTable(logPopulationSizes10Days, logMeanPopulationSizes10Days, overEstimate=log10(2000+1), file=file.path(dir, "table-1c.csv"))
logTable3$MeanProp <- table3$MeanProp; logTable3$SDProp <- table3$SDProp; 
write.csv(logTable3, file=file.path(dir, "table-3a.csv"))
```

>>>>

prettyScenario <- function(scenario) substr(scenario, 1, 1)
prettyModelName <- function(x) {
  lookup <- data.frame(x=modelNames, y=c("ST", "T", "TA", "FMP"), stringsAsFactors=F)
  lookup$y[match(x, lookup$x)]
}

@@

  print(p)
  return(p)
}
```

```{r figure-3-init-2}
registerDoMC(cores=10) # The nodes seem to run out of memory and fail with a bogus error message, so it's better to reduce the number of used cores.
populationSizes <- getPopulationSizes(scenarios=scenarios, modelNames=modelNames)
populationSizes2000 <- getPopulationSizes(scenarios=paste0(scenarios, "combined"), modelNames=modelNames)
populationSizes10Days <- getPopulationSizes(scenarios=paste0(scenarios, "10days"), modelNames=modelNames)

@@

```{r figure-3abc}
#modelNames <- modelNames[c(2:4,1)]

xlim <- log10(10^c(0,4)); ylim <- xlim
p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[1]), subset(logMeanPopulationSizes, modelName==modelNames[1]), modelName=modelNames[1], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3a1.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[2]), subset(logMeanPopulationSizes, modelName==modelNames[2]), modelName=modelNames[2], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3a2.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[3]), subset(logMeanPopulationSizes, modelName==modelNames[3]), modelName=modelNames[3], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3a3.png", width=8, height=4)

@@

dir <- normalizePath(context$figuresDirectory)
table1 <- getPopulationSizesTable(populationSizes, meanPopulationSizes, overEstimate=2000)
logTable1 <- getPopulationSizesTable(logPopulationSizes, logMeanPopulationSizes, overEstimate=log10(2000+1), file=file.path(dir, "table-1a.csv"))
logTable1$MeanProp <- table1$MeanProp; logTable1$SDProp <- table1$SDProp;

table2 <- getPopulationSizesTable(populationSizes2000, meanPopulationSizes2000, overEstimate=20000)
logTable2 <- getPopulationSizesTable(logPopulationSizes2000, logMeanPopulationSizes2000, overEstimate=log10(20000+1), file=file.path(dir, "table-1b.csv"))
logTable2$MeanProp <- table2$MeanProp; logTable2$SDProp <- table2$SDProp;

table3 <- getPopulationSizesTable(populationSizes10Days, meanPopulationSizes10Days, overEstimate=2000)
logTable3 <- getPopulationSizesTable(logPopulationSizes10Days, logMeanPopulationSizes10Days, overEstimate=log10(2000+1), file=file.path(dir, "table-1c.csv"))
logTable3$MeanProp <- table3$MeanProp; logTable3$SDProp <- table3$SDProp;

write.csv(logTable1, file=file.path(dir, "table-1a.csv"))
write.csv(logTable2, file=file.path(dir, "table-2a.csv"))
write.csv(logTable3, file=file.path(dir, "table-3a.csv"))
```
